Can We Crunch the Social Graph on the Cheap?

### 2011-01-26 doc/hotpar2011/softxmt-hotpar2011.tex
rewritten abstract (mark 2)

\maketitle
\begin{abstract}

  Large, sparse, irregular graphs map poorly to the memory systems of
  commodity hardware. The scale of emerging real world datasets
  demands new techniques; especially in the parallel case,
  straightforward algorithms will run inefficiently due to many
  high-latency accesses.  Pervasive parallelism can tolerate that
  latency, but the only large-scale implementation of the technique is
  the Cray XMT, an expensive, non-commodity machine.

>>>>

\maketitle
\begin{abstract}
  Large, sparse, irregular graphs map poorly to the memory systems of
  commodity hardware. The scale of emerging real world datasets
  presents a challenge for straightforward algorithms which will run
  inefficiently due to many high-latency accesses.  Pervasive
  parallelism can tolerate that latency, but the only large-scale
  implementation of the technique is the Cray XMT, an expensive,
  non-commodity machine.
